---
title: "ODAL simulation (Bias)"
author: "Jessie Tong"
date: "4/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Code Block 1, Results = 'hide',echo=FALSE}
Result_setting1 = read.csv('one_var/Result_setting1.csv')[,-1]
Result_setting2 = read.csv('one_var/Result_setting2.csv')[,-1]
Result_setting3 = read.csv('one_var/Result_setting3.csv')[,-1]
Result_setting4 = read.csv('one_var/Result_setting4.csv')[,-1]
```

```{r Code Block 2, message=FALSE, warning=FALSE,echo=FALSE}
#plotly
library(plotly)
beta_true = c(1,-1)
nn1 = seq(100,1000,by=100)
one_var <- function(Result_setting){
  R1_plot = cbind(Result_setting[,3],Result_setting[,5],Result_setting[,7], 
                  Result_setting[,9], Result_setting[,11], Result_setting[,13],
                  Result_setting[,15],Result_setting[,17],Result_setting[,22],nn1)
  R1_plot[,1:9] = R1_plot[,1:9] - matrix(beta_true[2], nrow = 10, ncol = 9)
  temp = rep(0,10)
  names(temp) =c("ODAL1 mean #1-9","ODAL1 median #1-9","ODAL1 mean","ODAL1 median", 
                 "ODAL2 mean mean", "ODAL2 mean median", "ODAL2 median mean", "ODAL2 median median",
                 "Meta","n")
  temp = cbind(t(t(temp)),t(R1_plot))
  R1_plot = t(temp)
  R1_plot = R1_plot[2:11,]
  DR1_PE <- as.data.frame(R1_plot[,c(1:10)])
  
  # plot
  p <- plot_ly(DR1_PE, 
               # odal 1 mean # 1-9
               x = DR1_PE$n, y = DR1_PE$`ODAL1 mean #1-9`, name = 'ODAL1 mean w/o hetero', type = 'scatter', mode = 'lines+markers'
               ,line = list(width = 3), symbols = c(16,15)) %>%
    #odal 1 mean
    add_trace(y = DR1_PE$`ODAL1 mean`, name = 'ODAL1 mean', mode = 'lines+markers',
              line = list( width = 3)) %>%
    #odal 2 mean mean
    add_trace(y = DR1_PE$`ODAL2 mean mean`, name = 'ODAL2 mean mean', mode = 'lines+markers',
              line = list(width = 3)) %>%
    #odal 2 mean median
    add_trace(y = DR1_PE$`ODAL2 mean median`, name = 'ODAL2 mean median', mode = 'lines+markers',
              line = list( width = 3)) %>%
    
    #odal 1 median # 1-9
    add_trace(y = DR1_PE$`ODAL1 median #1-9`, name = 'ODAL1 median w/o hetero', mode = 'lines+markers',
              line = list(width = 3)) %>%
    #odal 1 median
    add_trace(y = DR1_PE$`ODAL1 median`, name = 'ODAL1 median', mode = 'lines+markers',
              line = list(width = 3)) %>%
    #odal 2 median mean
    add_trace(y = DR1_PE$`ODAL2 median mean`, name = 'ODAL2 median mean', mode = 'lines+markers',
              line = list(width = 3)) %>%
    #odal 2 median median
    add_trace(y = DR1_PE$`ODAL2 median median`, name = 'ODAL2 median median', mode = 'lines+markers',
              line = list(width = 3)) %>%
    
    #Meta
    add_trace(y = DR1_PE$`Meta`, name = 'Meta', mode = 'lines+markers',
              line = list(width = 3, dash = "dash")) %>%
    
    layout(autosize = F, width = 1000, height = 500)
  return(p)
}

p1 <- one_var(Result_setting1)
p2 <- one_var(Result_setting2)
p3 <- one_var(Result_setting3)
p4 <- one_var(Result_setting4)
```
***
## Overall Setting
##### 1. 10 sites 
##### 2. each site size (nn) from 100 to 1,000
##### 3. total size (N) from 1,000 to 10,000
##### 4. replicates = 50


<br>

***
### One binary variable

***
#### Scenario 1: 1 out of 10 is heterogenous 

* Site #1 – 9 setting (including local site):
    + X1 = rbinom(N-nn,1,0.3)
    + Beta = (1, -1)
* Site #10 settings:
    + X1 = rbinom(nn,1,0.5)
    + Beta* = (1.5, -1)
```{r Code Block 3, message=FALSE, warning=FALSE, echo=FALSE}
p1
```


***
#### Scenario 2: 2 out of 10 is heterogenous 

* Site #1 – 8 setting (including local site):
    + X1 = rbinom(N-2*nn,1,0.3)
    + Beta = (1, -1)
* Site #9, 10 settings:
    + X1 = rbinom(2*nn,1,0.5)
    + Beta* = (1.5, -1)
```{r Code Block 4, message=FALSE, warning=FALSE, echo=FALSE}
p2
```


***
#### Scenario 3: 1 out of 10 is heterogenous

* Site #1 – 9 setting (including local site):
    + X1 = rbinom(N-nn,1,0.3)
    + Beta = (1, -1)
* Site #10 settings:
    + X1 = rbinom(nn,1,0.9)
    + Beta* = (3.0, -1)
```{r Code Block 5, message=FALSE, warning=FALSE, echo=FALSE}
p3
```


***
#### Scenario 4: 2 out of 10 is heterogenous 

* Site #1 – 8 setting (including local site):
    + X1 = rbinom(N-2*nn,1,0.3)
    + Beta = (1, -1)
* Site #9, 10 settings:
    + X1 = rbinom(2*nn,1,0.9)
    + Beta* = (3.0, -1)
```{r Code Block 6, message=FALSE, warning=FALSE, echo=FALSE}
p4
```

```{r Code Block 7, Results = 'hide',echo=FALSE}
Result_setting1_2 = read.csv('two_var/Result_setting1.csv')[,-1]
# Result_setting2_2 = read.csv('two_var/Result_setting2.csv')[,-1]
# Result_setting3_2 = read.csv('two_var/Result_setting3.csv')[,-1]
# Result_setting4_2 = read.csv('two_var/Result_setting4.csv')[,-1]
```

```{r Code Block 8, message=FALSE, warning=FALSE,echo=FALSE}
#plotly
library(plotly)
beta_true = c(1,-1)
nn1 = seq(100,1000,by=100)
two_var <- function(Result_setting){
  R1_plot = cbind(Result_setting[,4],Result_setting[,7],Result_setting[,10], 
                  Result_setting[,13], Result_setting[,16], Result_setting[,19],
                  Result_setting[,22],Result_setting[,25],Result_setting[,32],nn1)
  R1_plot[,1:9] = R1_plot[,1:9] - matrix(beta_true[2], nrow = 10, ncol = 9)
  temp = rep(0,10)
  names(temp) =c("ODAL1 mean #1-9","ODAL1 median #1-9","ODAL1 mean","ODAL1 median", 
                 "ODAL2 mean mean", "ODAL2 mean median", "ODAL2 median mean", "ODAL2 median median",
                 "Meta","n")
  temp = cbind(t(t(temp)),t(R1_plot))
  R1_plot = t(temp)
  R1_plot = R1_plot[2:11,]
  DR1_PE <- as.data.frame(R1_plot[,c(1:10)])
  
  # plot
  p <- plot_ly(DR1_PE, 
               # odal 1 mean # 1-9
               x = DR1_PE$n, y = DR1_PE$`ODAL1 mean #1-9`, name = 'ODAL1 mean #1-9', type = 'scatter', mode = 'lines+markers'
               ,line = list(width = 3), symbols = c(16,15)) %>%
    #odal 1 mean
    add_trace(y = DR1_PE$`ODAL1 mean`, name = 'ODAL1 mean', mode = 'lines+markers',
              line = list( width = 3)) %>%
    #odal 2 mean mean
    add_trace(y = DR1_PE$`ODAL2 mean mean`, name = 'ODAL2 mean mean', mode = 'lines+markers',
              line = list(width = 3)) %>%
    #odal 2 mean median
    add_trace(y = DR1_PE$`ODAL2 mean median`, name = 'ODAL2 mean median', mode = 'lines+markers',
              line = list( width = 3)) %>%
    
    #odal 1 median # 1-9
    add_trace(y = DR1_PE$`ODAL1 median #1-9`, name = 'ODAL1 median #1-9', mode = 'lines+markers',
              line = list(width = 3)) %>%
    #odal 1 median
    add_trace(y = DR1_PE$`ODAL1 median`, name = 'ODAL1 median', mode = 'lines+markers',
              line = list(width = 3)) %>%
    #odal 2 median mean
    add_trace(y = DR1_PE$`ODAL2 median mean`, name = 'ODAL2 median mean', mode = 'lines+markers',
              line = list(width = 3)) %>%
    #odal 2 median median
    add_trace(y = DR1_PE$`ODAL2 median median`, name = 'ODAL2 median median', mode = 'lines+markers',
              line = list(width = 3)) %>%
    
    #Meta
    add_trace(y = DR1_PE$`Meta`, name = 'Meta', mode = 'lines+markers',
              line = list(width = 3, dash = "dash")) %>%
    
    layout(autosize = F, width = 1000, height = 500)
  return(p)
}

p1_2 <- two_var(Result_setting1_2)
# p2 <- one_var(Result_setting2)
# p3 <- one_var(Result_setting3)
# p4 <- one_var(Result_setting4)
```
<br>

***
### Two variables

***
#### Scenario 1: 1 out of 10 is heterogenous 

* Site #1 – 9 setting (including local site):
    + X1 = rborn(N-nn)
    + X2 = rbinom(N-nn,1,0.3)
    + Beta = (1, 1, -1)
* Site #10 settings:
    + X1 = rborn(N-nn,1,1)
    + X2 = rbinom(nn,1,0.5)
    + Beta* = (1.5, 0.8, -1)
```{r Code Block 9, message=FALSE, warning=FALSE, echo=FALSE}
p1_2
```


